%---------------------------------------------------
% Nombre: bibliografia.tex  
% 
% Bibliografia
%---------------------------------------------------

\begin{thebibliography}{99}


\bibitem{com}
	\emph{} Moosavi, S.A. and Jalali, M. Community detection in online social networks using actions of users. 2014 Iranian Conference on Intelligent Systems, ICIS 2014.

\bibitem{sent}
	\emph{} Kyunglag Kwon, Yunwan Jeon, Chanho Cho, Jongwoo Seo, In-Jeong Chung, Hansaem Park: Sentiment trend analysis in social web environments. BigComp 2017: 261-268

\bibitem{sent2}
	\emph{} María del Pilar Salas-Zárate, José Medina-Moreira, Katty Lagos-Ortiz, Harry Luna-Aveiga, Miguel Ángel Rodríguez-García, Rafael Valencia-García: Sentiment Analysis on Tweets about Diabetes: An Aspect-Level Approach. Comp. Math. Methods in Medicine 2017: 5140631:1-5140631:9 (2017)
	
\bibitem{analitica}	
	\emph{} Serrano-Cobos, Jorge Big data y analítica web. Estudiar las corrientes y pescar en un océano de datos. El profesional de la información, 2014, vol. 23, n. 6, pp. 561-565.

\bibitem{finance}
	\emph{} E. W. T. Ngai, Yong Hu, Y. H. Wong, Yijun Chen, and Xin Sun. 2011. The application of data mining techniques in financial fraud detection: A classification framework and an academic review of literature. Decis. Support Syst. 50, 3 (February 2011), 559-569. 

\bibitem{liu1}
	\emph{} Pritam Gundecha, Huan Liu. Mining Social Media: A Brief Introduction. Arizona State University, Tempe, Arizona 85287.

\bibitem{liu}
	\emph{} B Liu, L Zhang . A survey of opinion mining and sentiment analysis - Mining text data, 2012. Springer.
	
\bibitem{diff}
	\emph{} Noferesti, Samira AND Shamsfard, Mehrnoush. Resource Construction and Evaluation for Indirect Opinion Mining of Drug Reviews. PLOS ONE, 2015. 
	

\bibitem{diff2}
	\emph{}Cambria E, Speer R, Havasi C, Hussain A. SenticNet: A publicly available semantic resource for opinion mining. In: AAAI CSK. 2010;14?8.

	
\bibitem{mkt}
	\emph{} Baier D., Daniel I. (2012) Image Clustering for Marketing Purposes. In: Gaul W., Geyer-Schulz A., Schmidt-Thieme L., Kunze J. (eds) Challenges at the Interface of Data Analysis, Computer Science, and Optimization. Studies in Classification, Data Analysis, and Knowledge Organization. Springer, Berlin, Heidelberg

\bibitem{agrawal}
	\emph{} Rakesh Agrawal, Tomasz Imieli?ski, and Arun Swami. 1993. Mining association rules between sets of items in large databases. SIGMOD Rec. 22, 2 (June 1993), 207-216. 

\bibitem{reglas1}
	\emph{} Pratibha Mandave, Megha Mane, Sharada Patil. Data mining using Association rule based on APRIORI algorithm and improved approach with illustration. International Journal of Latest Trends in Engineering and Technology (IJLTET), Vol. 3 Issue2 November 2013.

\bibitem{reglas2}
	\emph{}  Yong Yin, Ikou Kaku, Jiafu Tang, JianMing Zhu. Data Mining. Chapter 2, Association Rules Mining in Inventory Database (pp 9-23). Springer, 2011. 


\bibitem{sentimientos}
	\emph{} Rahim Dehkharghani, Hanefi Mercan, Arsalan Javeed, Yücel Saygin: Sentimental causal rule discovery from Twitter. Expert Syst. Appl. 41(10): 4950-4958 (2014)

\bibitem{mining1}	
	\emph{}Han, J.W. and Kamber, M. (2001) Data Mining: Concepts and Techniques. Morgan Kaufmann Pulishers, Inc., San Francisco.

\bibitem{mining2}
	\emph{}Tan, P.N., Steinbach, M. and Kumar, V. (2006) Introduction to Data Mining. Pearson Education, Inc., London, 30-336.	
	
\bibitem{mining3}
	\emph{}Wonchul Seo, Janghyeok Yoon, Hyunseok Park, Byoung-youl Coh, Jae-Min Lee, Oh-Jin Kwon. Product opportunity identification based on internal capabilities using text mining and association rule mining. Technological Forecasting \& Social Change 105 (2016) 94?104.	
	
\bibitem{mining4}
	\emph{}Manpreet Kaura, Shivani Kanga. Market Basket Analysis: Identify the changing trends of market data using association rule mining. International Conference on Computational Modeling and Security (CMS 2016). Procedia Computer Science 85 (2016) 78 ? 85. 
		
\bibitem{bigdata1}	
	\emph{} K. Jayabal, Dr. P. Marikkannu. An Efficient Big Data processing for frequent itemset mining based on MapReduce Framework.  International Journal of Novel Research in Computer Science and Software Engineering Vol. 3, Issue 1, pp: (130-134).

\bibitem{bigdata5}	
	\emph{}Lin, Ming-Yen and Lee, Pei-Yu and Hsueh, Sue-Chen. Apriori-based Frequent Itemset Mining Algorithms on MapReduce. ICUIMC '12, 2012. pp(76:1-76:8).

\bibitem{bigdata2}
	\emph{}X. Zhou and Y. Huang, An improved parallel association rules algorithm based on MapReduce framework for big data, 2014 11th International Conference on Fuzzy Systems and Knowledge Discovery (FSKD), Xiamen, 2014, pp. 284-288.

\bibitem{bigdata3}
	\emph{}Yunliang Chen, Fangyuan Li, Junqing Fan. (2015) Mining association rules in big data with NGEP. Cluster Computing 18:2, 577-585.
	
\bibitem{bigdata4}
	\emph{}Dr. R Nedunchezhian and K Geethanandhini. Association Rule Mining on Big Data. International Journal of Engineering Research \& Technology (IJERT). Volume. 5 - Issue. 05. (2015)
	
\bibitem{redes1}
	\emph{}Mariam Adedoyin-Olowe, Mohamed Medhat Gaber, Frederic T. Stahl: A Survey of Data Mining Techniques for Social Media Analysis. JDMDH 2014 (2014)


\bibitem{redes2}
	\emph{} Yiheng Zhou, Numair Sani, Chia-Kuei Lee, Jiebo Luo: Understanding Illicit Drug Use Behaviors by Mining Social Media. CoRR abs/1604.07096 (2016)
	
\bibitem{redes3}
	\emph{}Luca Cagliero and Alessandro Fiori. Analyzing Twitter User Behaviors and Topic Trends by Exploiting Dynamic Rules. Behavior Computing: Modeling, Analysis, Mining and Decision. Springer, 2012  pp. 267-287

\bibitem{redes4}
	\emph{} Luca Maria Aiello, Georgios Petkos, Carlos J. Martín, David Corney, Symeon Papadopoulos, Ryan Skraba, Ayse Göker, Ioannis Kompatsiaris, Alejandro Jaimes:
Sensing Trending Topics in Twitter. IEEE Trans. Multimedia 15(6): 1268-1282 (2013)

\bibitem{estadoarte1}
	\emph{}Zahra Farzanyar, Nick Cercone: Efficient mining of frequent itemsets in social network data based on MapReduce framework. ASONAM 2013: 1183-1188


\bibitem{estadoarte2}
	\emph{} S. Gole and B. Tidke, Frequent itemset mining for Big Data in social media using ClustBigFIM algorithm, 2015 International Conference on Pervasive Computing (ICPC), Pune, 2015, pp. 1-6.
	
	
\bibitem{bigfim}
	\emph{} Sandy Moens, Emin Aksehirli, Bart Goethals: Frequent Itemset Mining for Big Data. BigData Conference 2013: 111-118
	
\bibitem{estadoarte3}
	\emph{}Jie Yang and Brian Yecies. Open AccessMining Chinese social media UGC: a bigdata framework for analyzing Douban movie reviews, 2016, Journal of Big Data, vol 1. 

\bibitem{estadoarte4}
	\emph{} Xiaoqing Yu, Shimin Miao, Huanhuan Liu, Jenq-Neng Hwang, Wanggen Wan, Jing Lu: Association Rule Mining of Personal Hobbies in Social Networks. Int. J. Web Service Res. 14(1): 13-28 (2017)
		
\bibitem{estadoarte5}
	\emph{} Fredrik Erlandsson, Piotr Bródka, Anton Borg, Henric Johnson: Finding Influential Users in Social Media Using Association Rule Learning. Entropy 18(5): 164 (2016)

\end{thebibliography}
%---------------------------------------------------